---
title: "Assembly Report"
author:
    -
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
   rmd: "report.Rmd"
output:
  html_document:
    highlight: tango
    number_sections: no
    theme: default
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

----

# Global Asm4pg assembly report for:  `r snakemake@params[["sample"]]`
## Asm4pg Parameters
* Hifiasm mode : `r snakemake@params[["mode"]]`
* If hi-c or trio mode : 
  * parent1/r1 `r snakemake@params[["r1"]]`
  * parent2/r2 `r snakemake@params[["r2"]]`

* Hifiasm purge force : `r snakemake@params[["assembly_purge_force"]]` 
* Purge_dups executed: `r if (snakemake@params[["purge_dups_bool"]]) { "Yes" } else { "No" }`
* Genome scafolded: `r if (snakemake@params[["ragtag_bool"]]) { "Yes" } else { "No" }`

* Busco lineage: `r snakemake@params[["busco_lineage"]]`
* Genome ploidy: `r snakemake@params[["ploidy"]]`
* Kmers size: `r snakemake@params[["kmer_size"]]`

## Raw data QC
![](`r snakemake@input[["genomescope"]]`)

### Reads statistics
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["genometools_on_raw_data"]]), sep = '\n')
```

## QC on final assembly
### Assembly statistics
#### Hap 1
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["genometools_hap1"]]), sep = '\n')
```

#### Hap 2
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["genometools_hap2"]]), sep = '\n')
```

### K-mer profiles
| Hap 1 | Hap 2 |
|-------|-------|
| ![](`r snakemake@input[["kplot_hap1"]]`) | ![](`r snakemake@input[["kplot_hap2"]]`) |

### K-mer completeness and error rate
Completeness

```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["merqury_stats"]]), sep = '\n')
```

Error rate 
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["merqury_qv"]]), sep = '\n')
```

### BUSCO score
#### Hap 1
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["busco_hap1"]]), sep = '\n')
```
#### Hap 2
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["busco_hap2"]]), sep = '\n')
```

### Telomeres
Telomeres present in assembly
#### Hap 1
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["telomeres_hap1"]]), sep = '\n')
```
#### Hap 2
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["telomeres_hap2"]]), sep = '\n')
```

### Transposable element analysis
#### Hap 1
LTR recap
```{r comment='', echo=FALSE}
cat(head(readLines(snakemake@input[["LRT_recap_hap1"]]), 50), sep = '\n')
```
LAI
```{r comment='', echo=FALSE}
cat(head(readLines(snakemake@input[["LAI_hap1"]]), 2), sep = '\n')
```
#### Hap 2
LTR recap
```{r comment='', echo=FALSE}
cat(head(readLines(snakemake@input[["LRT_recap_hap2"]]), 50), sep = '\n')
```
LAI
```{r comment='', echo=FALSE}
cat(head(readLines(snakemake@input[["LAI_hap2"]]), 2), sep = '\n')
```