---
title: "Assembly Report"
author:
    -
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
   rmd: "report.Rmd"
output:
  html_document:
    highlight: tango
    number_sections: no
    theme: default
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

----

# `r snakemake@params[["id"]]` - run: `r snakemake@params[["run"]]`
* Run : `r snakemake@params[["run"]]`
* Hifiasm mode : `r snakemake@params[["mode"]]`

----

## Raw data QC
![](`r snakemake@input[["genomescope"]]`)

### Reads statistics
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["gt_reads"]]), sep = '\n')
```


## Assembly QC - Hifiasm
### Assembly statistics
#### Hap 1
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["gt_asm_1"]]), sep = '\n')
```

#### Hap 2
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["gt_asm_2"]]), sep = '\n')
```

### K-mer profiles
| Hap 1 | Hap 2 |
|-------|-------|
| ![](`r snakemake@input[["kplot_1"]]`) | ![](`r snakemake@input[["kplot_2"]]`) |

### K-mer completeness and error rate
Completeness

```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["merq_comp"]]), sep = '\n')
```

Error rate 
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["merq_err"]]), sep = '\n')
```

### BUSCO
#### Hap 1
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["busco_1"]]), sep = '\n')
```
#### Hap 2
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["busco_2"]]), sep = '\n')
```

### Telomeres
Telomeres present in assembly

#### Hap 1
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["tel_1"]]), sep = '\n')
```
#### Hap 2
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["tel_2"]]), sep = '\n')
```

### LTR Assembly Index (LAI) 
#### Hap 1
LTR recap
```{r comment='', echo=FALSE}
cat(head(readLines(snakemake@input[["LRT_recap_1"]]), 50), sep = '\n')
```
LAI
```{r comment='', echo=FALSE}
cat(head(readLines(snakemake@input[["LAI_1"]]), 2), sep = '\n')
```
#### Hap 2
LTR recap
```{r comment='', echo=FALSE}
cat(head(readLines(snakemake@input[["LRT_recap_2"]]), 50), sep = '\n')
```
LAI
```{r comment='', echo=FALSE}
cat(head(readLines(snakemake@input[["LAI_2"]]), 2), sep = '\n')
```

## Assembly QC - After Purge_dups
### Assembly statistics
#### Hap 1
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["P_gt_asm_1"]]), sep = '\n')
```

#### Hap 2
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["P_gt_asm_2"]]), sep = '\n')
```
### K-mer profiles
| Hap 1 | Hap 2 |
|-------|-------|
| ![](`r snakemake@input[["P_kplot_1"]]`) | ![](`r snakemake@input[["P_kplot_2"]]`) |

### K-mer completeness and error rate
Completeness

```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["P_merq_comp"]]), sep = '\n')
```

Error rate 
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["P_merq_err"]]), sep = '\n')
```

### BUSCO
#### Hap 1
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["P_busco_1"]]), sep = '\n')
```
#### Hap 2
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["P_busco_2"]]), sep = '\n')
```

### Telomeres
Telomeres present in assembly

#### Hap 1
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["P_tel_1"]]), sep = '\n')
```
#### Hap 2
```{r comment='', echo=FALSE}
cat(readLines(snakemake@input[["P_tel_2"]]), sep = '\n')
```

### LTR Assembly Index (LAI) 
#### Hap 1
LTR recap
```{r comment='', echo=FALSE}
cat(head(readLines(snakemake@input[["P_LRT_recap_1"]]), 50), sep = '\n')
```
LAI
```{r comment='', echo=FALSE}
cat(head(readLines(snakemake@input[["P_LAI_1"]]), 2), sep = '\n')
```
#### Hap 2
LTR recap
```{r comment='', echo=FALSE}
cat(head(readLines(snakemake@input[["P_LRT_recap_2"]]), 50), sep = '\n')
```
LAI
```{r comment='', echo=FALSE}
cat(head(readLines(snakemake@input[["P_LAI_2"]]), 2), sep = '\n')
```
